---
title: "Replication of Faber's A Quantitative Approach to Tactical Asset Allocation - South Africa"
output: html_notebook
---

####Importing the data into R

Each asset's class price series has been saved as a CSV. The packages used for performance analysis and backtesting require the data to be xts objects which are created by the following code.

```{r, message=FALSE, warning=FALSE}
#remove past data
rm(list = ls(envir = globalenv()),envir = globalenv()) #clear Vars from global enviroment

#Load required packages
library(PerformanceAnalytics)
library(quantstrat)

#declare symbols
symbols <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","BITCOIN","CPI")

#use quantmod function to load data as xts objects
getSymbols(symbols,
           src = "csv",
           dir="../Data/CSV files",
           col.names=c("Close"))

#Define subset dates for different period
SubsetPeriod.Reporting <- "2011-12-31::2016-12-31"
SubsetPeriod.Calculations <- "2010-12-31::2016-12-31"
```

#### Calculating asset class returns and charting

Once the data is loaded we can create one xts object for the prices and calculate each asset class's returns. The asset class returns are then charted.
```{r}
#combine all closing prices into one xts file
AllAssets <- cbind.xts(Cl(TBILLS),
                       Cl(SP500),
                       Cl(EAFE),
                       Cl(US10YR),
                       Cl(GSCI),
                       Cl(NAREIT),
                       Cl(BITCOIN),
                       Cl(CPI))                       
                      

AllAssets <- AllAssets[SubsetPeriod.Reporting]
colnames(AllAssets) <- symbols

#calculate returns and cum returns
AllAssets.ret <- Return.calculate(AllAssets)[-1,]
AllAssets.cumret <- 100*cumprod(1+ ROC(AllAssets, type = "discrete")[-1,])
#how do i add a row at the top with value of 100 for each? rbind?

chart.TimeSeries(AllAssets.cumret[SubsetPeriod.Reporting],
 main = paste("Figure X - SA Asset Class Returns, Log Scale",sep = ""),
 ylab = "",
 #ylog = TRUE,
 #ylim = c(100,250000),
 #date.format = "%Y",
 major.ticks = "years",
 legend.loc = "topleft",
 colorset = c("orangered3","olivedrab","slateblue","blue","gold2","dodgerblue2","cornflowerblue")
 #minor.ticks =FALSE
 )

#scale bitcoin on another axis??
```


####Analysing asset class returns, max drawdowns and other performance statistics

Using the package performance analytics, common performance statistics such as CAGR, volatility and sharpe ratios can be calculated.
```{r}
#Create xts for Returns
Returns <- AllAssets.ret[SubsetPeriod.Reporting]

#calculate statistics and store as "stats"
stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = AllAssets.ret$TBILLS),
               100*maxDrawdown(Returns,scale = 12,invert = FALSE),
               100*c(Return.annualized(Returns$CPI,scale = 12)))

#rename table rows/column names and format
colnames(stats) <- symbols
row
names(stats) <- c("Return",
                  "Volatility",
                  paste("Sharpe (",round(stats[1,"TBILLS"],2),"%)", sep = ""),
                  "MaxDD",
                  "Inflation CAGR")

stats <- round(stats[,-8],2) #delete inflation column - change to 7 when including property.

#print
stats

#copies stats to clipboad for pasting into word/excel
#write.table(stats, "clipboard", sep="\t", col.names=NA) 
```

####Managing Risk 

Lets chart each asset with its 10 month simple moving average

```{r}
myChart_Theme <- chart_theme() #Create a chart_theme
myChart_Theme$col$line.col <- "blue"

SMAperiod <- 10

chart_Series(Cl(BITCOIN),
  name = paste("BITCOIN vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

#change to other chart so can make it log?
```

####Calculating returns

```{r, message=FALSE, warning=FALSE}
#Import saved pricing data csv files as xts
getSymbols("TBILLYIELDS",
           src = "csv",
           dir="../Data/CSV files/",
           col.names=c("Close"))

#load an additional library
library(dplyr)

#Create new all assets
AllAssets <- cbind.xts(Cl(SP500),
                       Cl(EAFE),
                       Cl(US10YR),
                       Cl(GSCI),
                       Cl(NAREIT),
                       Cl(BITCOIN),
                       Cl(TBILLYIELDS)) 


AllAssets <- AllAssets[SubsetPeriod.Calculations]

#create dataframe - tidyverse not compatible with xts?
AllAssets.df <- data.frame(date=index(AllAssets), coredata(AllAssets)) #, row.names = index(AllAssets))

bandwidth <- 0.02
#mutate new columns


AllAssets.df  <- mutate(AllAssets.df,
  "RF.ret" =  c(0,lag((TBILLYIELDS.Close/100)/12)[-1]), 

  "SP500.ret" =  c(0,diff(SP500.Close)/lag(SP500.Close)[-1]),
  "SP500.10m.SMA" =  rollmean(SP500.Close,10,fill = 0,align = "right"),
  "SP500.10m.signal" =  lag(ifelse(SP500.Close>=SP500.10m.SMA,1,0)),
  "SP500.10m.timingret" = ifelse(SP500.10m.signal == 1,SP500.ret,RF.ret),
  
  "EAFE.ret" =  c(0,diff(EAFE.Close)/lag(EAFE.Close)[-1]),
  "EAFE.10m.SMA" =  rollmean(EAFE.Close,10,fill = 0,align = "right"),
  "EAFE.10m.signal" =  lag(ifelse(EAFE.Close>=EAFE.10m.SMA,1,0)),
  "EAFE.10m.timingret" = ifelse(EAFE.10m.signal == 1,EAFE.ret,RF.ret),
  
  "US10YR.ret" =  c(0,diff(US10YR.Close)/lag(US10YR.Close)[-1]),
  "US10YR.10m.SMA" =  rollmean(US10YR.Close,10,fill = 0,align = "right"),
  "US10YR.10m.signal" =  lag(ifelse(US10YR.Close>=US10YR.10m.SMA,1,0)),
  "US10YR.10m.timingret" = ifelse(US10YR.10m.signal == 1,US10YR.ret,RF.ret),
  
  "GSCI.ret" =  c(0,diff(GSCI.Close)/lag(GSCI.Close)[-1]),
  "GSCI.10m.SMA" =  rollmean(GSCI.Close,10,fill = 0,align = "right"),
  "GSCI.10m.signal" =  lag(ifelse(GSCI.Close>=GSCI.10m.SMA,1,0)),
  "GSCI.10m.timingret" = ifelse(GSCI.10m.signal == 1,GSCI.ret,RF.ret),

  "NAREIT.ret" =  c(0,diff(NAREIT.Close)/lag(NAREIT.Close)[-1]),
  "NAREIT.10m.SMA" =  rollmean(NAREIT.Close,10,fill = 0,align = "right"),
  "NAREIT.10m.signal" =  lag(ifelse(NAREIT.Close>=NAREIT.10m.SMA,1,0)),
  "NAREIT.10m.timingret" = ifelse(NAREIT.10m.signal == 1,NAREIT.ret,RF.ret),

  "BITCOIN.ret" =  c(0,diff(BITCOIN.Close)/lag(BITCOIN.Close)[-1]),
  "BITCOIN.10m.SMA" =  rollmean(BITCOIN.Close,10,fill = 0,align = "right"),
  "BITCOIN.10m.signal" =  lag(ifelse(BITCOIN.Close>=BITCOIN.10m.SMA,1,0)),
  "BITCOIN.10m.timingret" = ifelse(BITCOIN.10m.signal == 1,BITCOIN.ret,RF.ret),
  
  "BuyandHold.ret" = (SP500.ret + EAFE.ret + US10YR.ret + GSCI.ret + NAREIT.ret + BITCOIN.ret)/5*0.95 + 0.05* BITCOIN.ret,
  "Timing.ret" = (SP500.10m.timingret + EAFE.10m.timingret + US10YR.10m.timingret + GSCI.10m.timingret + NAREIT.10m.timingret)/5*0.95 + 0.05 * BITCOIN.10m.timingret
  )



rownames(AllAssets.df) <- index(AllAssets)

#Create xts of calculations to analyse performance
AllAssets.xts <- xts(AllAssets.df[,-1], order.by = AllAssets.df$date)

#detach the packagae dplyr as it isn't compatible with other packages?
detach(package:dplyr)
```

#### Individual Asset Class Comparisons

```{r}
#for calculating the sharpe ratio later
Rf.ret <- Return.calculate(TBILLYIELDS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod.Reporting]

Returns <- cbind.xts(AllAssets.xts$BITCOIN.ret, 
                     AllAssets.xts$BITCOIN.10m.timingret)[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy and Hold","Timing")
colnames(Returns) <- c("Buy and Hold","Timing")

#as.numeric(substr(SubsetPeriod,1,4))+1
chart.TimeSeries(CumReturns,
  main = paste("Buy and Hold vs Timing vs Timing Avg, ",
               substr(SubsetPeriod.Reporting,1,4),"-",
               substr(SubsetPeriod.Reporting,13,16),
               ", Log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(50,1000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE)

chart.Drawdown(Returns,#[,-1], to exclude B&H
  main = paste("Buy and Hold vs Timing vs Timing Avg",substr(SubsetPeriod.Reporting,1,4),"-",substr(SubsetPeriod.Reporting,13,16),", Non-log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2,3,5,6),
  ylab = "Drawdown",
  legend.loc = "bottomright",
  major.ticks = "years",
  minor.ticks = FALSE)

```

```{r}
stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLYIELDS.Close),
               maxDrawdown(Returns,scale = 12,invert = FALSE)*100,

                              # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               #Information Ratio
               InformationRatio(Returns, Returns$"Buy and Hold"),
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               #Calmar Ratio
               CalmarRatio(Returns["2014::2017"], scale = 12)
               
               )
               
colnames(stats) <- c("Buy and Hold","Timing")
rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe",
                     "MaxDD",
                     # "% Positive Months",
                     # "% Months invested in the Asset",
                     # "% Positive Months when invested",
                     "Sortino Ratio",
                     "Information Ratio",
                     "Ulcer Index",
                     "Calmar Ratio")

round(stats,2)
write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)

```

####GTAA Performance Charts

```{r}
Returns <- cbind.xts(AllAssets.xts$BuyandHold.ret,
                     AllAssets.xts$Timing.ret)[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","Timing")

chart.TimeSeries(CumReturns,
  main = "Figure X - Timing Model Comparison, Log Scale",
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(100,76000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE,
  yaxis = TRUE)

chart.TimeSeries(CumReturns,
  main = "Figure X - Timing Model Comparison, Non Log Scale",
  date.format = "%Y",
  colorset = c(4,2,3,5,6),
  ylab = "",
  ylog = FALSE,
  #ylim = c(100,500),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE)
```

```{r}
Rf.ret <- Return.calculate(TBILLS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod.Reporting]

Returns <- cbind.xts(AllAssets.xts$BuyandHold.ret,
                     AllAssets.xts$Timing.ret)[SubsetPeriod.Reporting]

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               100*maxDrawdown(Returns,invert = FALSE),
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod.Reporting],scale = 12)),
               
               # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               #Information Ratio
               InformationRatio(Returns, Returns$BuyandHold.ret),
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               #Calmar Ratio
               CalmarRatio(Returns["2014::2017"], scale = 12)
               )

colnames(stats) <- c("Buy & Hold",
                     "Timing")

rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe", #what %?
                     "MaxDD",
                     "Inflation CAGR",
                     "Sortino Ratio",
                     "Information Ratio",
                     "Ulcer Index",
                     "Calmar Ratio")

round(stats,2)
#write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)

```

