---
title: "Replication of Faber's A Quantitative Approach to Tactical Asset Allocation - Asset Class Returns"
output: html_notebook
---

####Importing the data into R

Each asset's class price series has been saved as a CSV. The packages used for performance analysis and backtesting require the data to be xts objects which are created by the following code.
```{r, message=FALSE, warning=FALSE}
#remove past data
rm(list = ls(envir = globalenv()),envir = globalenv()) #clear Vars from global enviroment

#Load required packages
library(PerformanceAnalytics)
library(quantstrat)

#Set Symbols
symbols <- c("RiskFree","DomesticEquity","GlobalEquity","FixedIncome","Commodities","RealEstate","CPI")

#Import saved pricing data csv files as xts
getSymbols(symbols,
           src = "csv",
           dir="../Data/CSV files/SA/",
           col.names=c("Close"))
```

#### Calculating asset class returns and charting

Once the data is loaded i can create one xts object for the prices and calculate each asset class's returns. The asset class returns are then charted.
```{r}
AllAssets <- cbind.xts(Cl(RISKFREE),
                       Cl(DOMESTICEQUITY),
                       Cl(GLOBALEQUITY),
                       Cl(FIXEDINCOME),
                       Cl(COMMODITIES),
                       Cl(REALESTATE),
                       Cl(CPI))                       

#subset to required period
SubsetPeriod <- "2003-06-30::2016-12-31"

AllAssets <- AllAssets[SubsetPeriod]
colnames(AllAssets) <- symbols

#calculate returns and cum returns
AllAssets.ret <- Return.calculate(AllAssets)[-1,]
AllAssets.cumret <- 100*cumprod(1+ ROC(AllAssets, type = "discrete")[-1,])

chart.TimeSeries(AllAssets.cumret[SubsetPeriod],
 main = paste("Figure X - SA Asset Class Returns ",substr(SubsetPeriod,1,4),"-",substr(SubsetPeriod,13,16),", Log Scale",sep = ""), 
 ylab = "",
 ylog = TRUE,
 ylim = c(80,2000),
 date.format = "%Y",
 major.ticks = "years",
 legend.loc = "topleft",
 colorset = c("orangered3","olivedrab","slateblue","blue","gold2","dodgerblue2","cornflowerblue"),
 minor.ticks =FALSE)
```

####Analysing asset class returns, max drawdowns and other performance statistics

Using the package performance analytics, common performance statistics such as CAGR, volatility and sharpe ratios can be calculated.
```{r}
#subset to required dates
#SubsetPeriod <- "1972-12-31::2012-12-31"

#Create xts for Returns
Returns <- AllAssets.ret[SubsetPeriod]

#calculate statistics and store as "stats"
stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = AllAssets.ret$RiskFree),
               100*maxDrawdown(Returns,scale = 12,invert = FALSE),
               100*c(Return.annualized(Returns$CPI,scale = 12)))

#rename table rows/column names and format
colnames(stats) <- symbols
rownames(stats) <- c("Return","Volatility",paste("Sharpe (",round(stats[1,"RiskFree"],2),"%)", sep = ""),"MaxDD","Inflation CAGR")
stats <- round(stats[,-7],2)
```

Lets print the stats:
```{r, echo=FALSE}
stats

#copies stats to clipboad for pasting into word/excel
write.table(stats, "clipboard", sep="\t", col.names=NA) 
```

####Managing Risk 

Lets chart each asset with its 10 month simple moving average

```{r}
myChart_Theme <- chart_theme() #Create a chart_theme
myChart_Theme$col$line.col <- "blue"

SMAperiod <- 10

chart_Series(Cl(DOMESTICEQUITY),
  name = paste("Domestic Equity vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(GLOBALEQUITY),
  name = paste("Gloabl Equity vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(FIXEDINCOME),
  name = paste("Fixed Income vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(COMMODITIES),
  name = paste("Commodities vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(REALESTATE),
  name = paste("Real Estate vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )
```

####Calculating returns

```{r, message=FALSE, warning=FALSE}

#Import saved pricing data csv files as xts
getSymbols("RiskFreeYields",
           src = "csv",
           dir="../Data/CSV files/SA/",
           col.names=c("Close"))

#load an additional library
library(dplyr)

#Create new all assets
AllAssets <- cbind.xts(Cl(DOMESTICEQUITY),
                       Cl(GLOBALEQUITY),
                       Cl(FIXEDINCOME),
                       Cl(COMMODITIES),
                       Cl(REALESTATE),
                       Cl(RISKFREEYIELDS))   

AllAssets <- AllAssets[SubsetPeriod]

#create dataframe - tidyverse not compatible with xts?
AllAssets.df <- data.frame(date=index(AllAssets), coredata(AllAssets)) #, row.names = index(AllAssets))

#mutate new columns
AllAssets.df  <- mutate(AllAssets.df,
  "DOMESTICEQUITY.SMA" =  rollmean(DOMESTICEQUITY.Close,10,fill = 0,align = "right"),
  "GLOBALEQUITY.SMA" =  rollmean(GLOBALEQUITY.Close,10,fill = 0,align = "right"),
  "FIXEDINCOME.SMA" =  rollmean(FIXEDINCOME.Close,10,fill = 0,align = "right"),
  "COMMODITIES.SMA" =  rollmean(COMMODITIES.Close,10,fill = 0,align = "right"),
  "REALESTATE.SMA" =  rollmean(REALESTATE.Close,10,fill = 0,align = "right"),
  "DOMESTICEQUITY.ret" =  c(0,diff(DOMESTICEQUITY.Close)/lag(DOMESTICEQUITY.Close)[-1]),
  "GLOBALEQUITY.ret" =  c(0,diff(GLOBALEQUITY.Close)/lag(GLOBALEQUITY.Close)[-1]),
  "FIXEDINCOME.ret" =  c(0,diff(FIXEDINCOME.Close)/lag(FIXEDINCOME.Close)[-1]),
  "COMMODITIES.ret" =  c(0,diff(COMMODITIES.Close)/lag(COMMODITIES.Close)[-1]),
  "REALESTATE.ret" =  c(0,diff(REALESTATE.Close)/lag(REALESTATE.Close)[-1]),
  "RF.ret" =  lag((2*RISKFREEYIELDS.Close/100)/12),
  "DOMESTICEQUITY.signal" =  lag(ifelse(DOMESTICEQUITY.Close>=DOMESTICEQUITY.SMA,1,0)),
  "GLOBALEQUITY.signal" =  lag(ifelse(GLOBALEQUITY.Close>=GLOBALEQUITY.SMA,1,0)),
  "FIXEDINCOME.signal" =  lag(ifelse(FIXEDINCOME.Close>=FIXEDINCOME.SMA,1,0)),
  "COMMODITIES.signal" =  lag(ifelse(COMMODITIES.Close>=COMMODITIES.SMA,1,0)),
  "REALESTATE.signal" = lag(ifelse(REALESTATE.Close>=REALESTATE.SMA,1,0)),
  "DOMESTICEQUITY.timingret" = ifelse(DOMESTICEQUITY.signal == 1,DOMESTICEQUITY.ret,RF.ret),
  "GLOBALEQUITY.timingret" = ifelse(GLOBALEQUITY.signal == 1,GLOBALEQUITY.ret,RF.ret),
  "FIXEDINCOME.timingret" = ifelse(FIXEDINCOME.signal == 1,FIXEDINCOME.ret,RF.ret),
  "COMMODITIES.timingret" = ifelse(COMMODITIES.signal == 1,COMMODITIES.ret,RF.ret),
  "REALESTATE.timingret" = ifelse(REALESTATE.signal == 1,REALESTATE.ret,RF.ret),
  "GTAA.ret" = (DOMESTICEQUITY.timingret + GLOBALEQUITY.timingret + FIXEDINCOME.timingret + COMMODITIES.timingret + REALESTATE.timingret)/5,
  "BUYANDHOLD.ret" = (DOMESTICEQUITY.ret + GLOBALEQUITY.ret + FIXEDINCOME.ret + COMMODITIES.ret + REALESTATE.ret)/5
)

rownames(AllAssets.df) <- index(AllAssets)

#Create xts of calculations to analyse performance
AllAssets.xts <- xts(AllAssets.df[,-1], order.by = AllAssets.df$date)

#detach the packagae dplyr as it isn't compatible with other packages?
detach(package:dplyr)
```

####Performance Charts

```{r}
SubsetPeriod <- "2004-06-30::2016-12-31" 
Returns <- cbind.xts(AllAssets.xts$BUYANDHOLD.ret,AllAssets.xts$GTAA.ret)[SubsetPeriod]
CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns["1973-01-31::2016-12-31"],
  main = paste("Figure X - Buy & Hold vs Timing Model ",substr(SubsetPeriod,1,4),"-",substr(SubsetPeriod,13,16),", Log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2),
  ylab = "",
  ylog = TRUE,
  ylim = c(100,500),
  legend.loc = "left",
  major.ticks = "years",
  minor.ticks = FALSE)

chart.TimeSeries(CumReturns["1973-01-31::2016-12-31"],
  main = paste("Figure X - Buy & Hold vs Timing Model ",substr(SubsetPeriod,1,4),"-",substr(SubsetPeriod,13,16),", Non-log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2),
  ylab = "",
  ylog = FALSE,
  ylim = c(100,500),
  legend.loc = "left",
  major.ticks = "years",
  minor.ticks = FALSE)
```

need proper yield curve! 
how does this compare to USA?

```{r}
#SubsetPeriod <- "1973-01-31::2012-12-31" 
Returns <- cbind.xts(AllAssets.xts$BUYANDHOLD.ret,AllAssets.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               100*maxDrawdown(Returns,invert = FALSE),
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```

so better sharpe? [confirm calc method/fix interest rate... should i calc manually?] and less maxdd
whats kurtosis, information ratio, skew. ask what metrics rad, mb and emyln use...
run on longer dater in asset allocation ratios

last 12 months, 3 years, etc returns

rolling returns

to do:

* how to calculate dailyreturns with NA
* check returns make sense - effect of zar?
* compare to US / JPY
* create RF to get 2002 in

To do:
SA assets
Daily drawdowns
Relative performance / rolling perofrmance / alpha
10 worst periods / 10 best periods 
