---
title: "Global Tactical Asset Allocation"
output: html_notebook
---

Faber applies his market timing rule to an asset allocation of US Stocks, foreign stocks, bonds, real estate and commodities. 

#### The code
```{r, message=FALSE, warning=TRUE, include=FALSE}
#Load the required packages
library(PerformanceAnalytics)
library(quantmod)
library(dplyr)
library(ggplot2)

#Set the symbols required
symbols <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","CPI","TBILLYIELDS")

#Load the data
getSymbols(symbols,
           src = "csv",
           dir="../Data/CSV files",
           col.names=c("Close"))
```

```{r}
#Create an xts of all assets' prices
AssetPrices <- cbind.xts(Cl(SP500),
                         Cl(EAFE),
                         Cl(US10YR),
                         Cl(GSCI),
                         Cl(NAREIT),
                         Cl(TBILLYIELDS))

AssetPrices <- AssetPrices["1972-01-31::2016-12-31"]

#Create dataframe to perform calculations (seems tidyverse not compatible with xts?)
TimingModelCalcs <- data.frame(date=index(AssetPrices), coredata(AssetPrices))
TimingModelCalcs  <- mutate(TimingModelCalcs,
  "SP500.SMA" =  rollmean(SP500.Close,10,fill = 0,align = "right"),
  "EAFE.SMA" =  rollmean(EAFE.Close,10,fill = 0,align = "right"),
  "US10YR.SMA" =  rollmean(US10YR.Close,10,fill = 0,align = "right"),
  "GSCI.SMA" =  rollmean(GSCI.Close,10,fill = 0,align = "right"),
  "NAREIT.SMA" =  rollmean(NAREIT.Close,10,fill = 0,align = "right"),
  "SP500.ret" =  c(0,diff(SP500.Close)/lag(SP500.Close)[-1]),
  "EAFE.ret" =  c(0,diff(EAFE.Close)/lag(EAFE.Close)[-1]),
  "US10YR.ret" =  c(0,diff(US10YR.Close)/lag(US10YR.Close)[-1]),
  "GSCI.ret" =  c(0,diff(GSCI.Close)/lag(GSCI.Close)[-1]),
  "NAREIT.ret" =  c(0,diff(NAREIT.Close)/lag(NAREIT.Close)[-1]),
  "RF.ret" =  lag((TBILLYIELDS.Close/100)/12),
  "SP500.signal" =  lag(ifelse(SP500.Close>=SP500.SMA,1,0)),
  "EAFE.signal" =  lag(ifelse(EAFE.Close>=EAFE.SMA,1,0)),
  "US10YR.signal" =  lag(ifelse(US10YR.Close>=US10YR.SMA,1,0)),
  "GSCI.signal" =  lag(ifelse(GSCI.Close>=GSCI.SMA,1,0)),
  "NAREIT.signal" = lag(ifelse(NAREIT.Close>=NAREIT.SMA,1,0)),
  "SP500.timingret" = ifelse(SP500.signal == 1,SP500.ret,RF.ret),
  "EAFE.timingret" = ifelse(EAFE.signal == 1,EAFE.ret,RF.ret),
  "US10YR.timingret" = ifelse(US10YR.signal == 1,US10YR.ret,RF.ret),
  "GSCI.timingret" = ifelse(GSCI.signal == 1,GSCI.ret,RF.ret),
  "NAREIT.timingret" = ifelse(NAREIT.signal == 1,NAREIT.ret,RF.ret),
  "GTAA.ret" = (SP500.timingret + EAFE.timingret + US10YR.timingret + GSCI.timingret + NAREIT.timingret)/5,
  "BUYANDHOLD.ret" = (SP500.ret + EAFE.ret + US10YR.ret + GSCI.ret + NAREIT.ret)/5
)

#Create xts of calculations to analyse performance
TimingModelCalcs.xts <- xts(TimingModelCalcs[,-1], order.by = TimingModelCalcs$date)
```

Notes:

* Technically rebalances monthly - should look at quarterly or annual rebalances?

### Replicating the research 1973-2012

#### Time invested

```{r}
TimeInvestedCalcs <- transmute(TimingModelCalcs,
  "Date" = date,
  "AssetsInvested" =  SP500.signal +  EAFE.signal + US10YR.signal + GSCI.signal + NAREIT.signal
)

TimeInvestedCalcs.xts <- xts(TimeInvestedCalcs[,-1], order.by = TimeInvestedCalcs$Date)

SubsetPeriod <- "1972-12-31::2012-12-31"
TimeInvestedCalcs.xts <- TimeInvestedCalcs.xts[SubsetPeriod]

#Tabulate and turn into data.frame
TimeInvestedStats <- as.data.frame(table(TimeInvestedCalcs.xts))
TimeInvestedStats <- transform(TimeInvestedStats,
                  "Percentage of Months" = prop.table(Freq))

colnames(TimeInvestedStats) <- c("Number of Positions","# of Months","% of Months")
TimeInvestedStats$`% of Months` <- round(TimeInvestedStats$`% of Months`,4)*100
rownames(TimeInvestedStats) <- c("0% Invested (all cash)",
                                 "20% Invested",
                                 "40% Invested",
                                 "60% Invested",
                                 "80% Invested",
                                 "100% Invested (fully invested)")
TimeInvestedStats

paste("On average the investor is ", 
      round(20*sum(c(0,1,2,3,4,5) * TimeInvestedStats$`# of Months`) / sum(TimeInvestedStats$`# of Months`),2), 
      "% invested", sep ="")

BarChartData <- data.frame(date=index(TimeInvestedCalcs.xts), coredata(TimeInvestedCalcs.xts))
colnames(BarChartData) <- c("Date","InvestedAssets")
ggplot(data=BarChartData, aes(x=Date, y=InvestedAssets)) +
  geom_bar(stat = "identity", width = 20) + 
  labs(title = "Number of Assets Invested in at Time", x = "Year", y = "Assets")
```

* need to format better

####Performance Charts

```{r}
SubsetPeriod <- "1973-01-31::2012-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 1973-2012, log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = TRUE,
                 ylim = c(80,6000),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```

```{r}
chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 1973-2012, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(80,6000),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```


```{r}
SubsetPeriod <- "1973-01-31::2012-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               maxDrawdown(Returns,invert = FALSE)*100,
               c(100*Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
```
to do: 

* why sharpe ratio is different - use RF
* % positive months
* CAGR

### Yearly Returns

```{r}
SubsetPeriod <- "1972-12-31::2012-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
YearlyReturns <- cbind.xts(yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$BUYANDHOLD.ret[SubsetPeriod])),
                           yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$GTAA.ret[SubsetPeriod])))[-1,]

colnames(YearlyReturns) <- c("Buy & Hold","GTAA")

round(100*YearlyReturns,2)

YearlyStats <- rbind(Return.annualized(YearlyReturns)*100, 
               StdDev.annualized(YearlyReturns)*100, 
               SharpeRatio.annualized(YearlyReturns,Rf = 0.0541),
               maxDrawdown(YearlyReturns,invert = FALSE)*100,
               c(100*Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

round(YearlyStats,2)
```

Notes:

* see how stats differ for annual - drawdown underreported so check daily

#### Since 2012

Let's see how the strategy has performed since 2012


```{r}
SubsetPeriod <- "2013-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 2013-2016, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(75,125),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```

```{r}
SubsetPeriod <- "1973-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")
colnames(Returns) <- c("Buy & Hold","GTAA")
chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 1973-2016, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(80,6500),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```


```{r}
chart.Drawdown(Returns,
                 main = "Buy & Hold vs Timing Model Drawdowns, 1973-2016",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "Drawdown",
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

```


#### Yearly Returns since 2012
```{r}
SubsetPeriod <- "2012-12-31::2016-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
YearlyReturns <- cbind.xts(yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$BUYANDHOLD.ret[SubsetPeriod])),
                           yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$GTAA.ret[SubsetPeriod])))[-1,]

colnames(YearlyReturns) <- c("Buy & Hold","GTAA")
round(100*YearlyReturns,2)
```

#### Monthly Performance Stats since 2012

```{r}
SubsetPeriod <- "2013-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               maxDrawdown(Returns,invert = FALSE)*100,
               c(100*Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )
colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
```

Summary

* THE GTAA timing strategy continued to perform as it has in the past relative to the Buy and Hold strategy.
** From 2013 to 2016, although returns were slightly worse than the Buy and Hold there were with much less volatility and lower drawdowns.

