---
title: "Replication of Faber's A Quantitative Approach to Tactical Asset Allocation - Managing Risk"
output: html_notebook
---

####Importing the data into R

Each asset's class price series has been saved as a CSV. The packages used for performance analysis and backtesting require the data to be xts objects which are created by the following code.

```{r, message=FALSE}
#remove past data
rm(list = ls(envir = globalenv()),envir = globalenv()) #clear Vars from global enviroment

#load required packages
library(PerformanceAnalytics)
library(quantstrat)

#declare symbols
symbols <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","CPI")

#use quantmod function to load data as xts objects
getSymbols(symbols,
  src = "csv",
  dir="../Data/CSV files",
  col.names=c("Close"))

#also load TBILL YIELDS
getSymbols("TBILLYIELDS",
  src = "csv",
  dir="../Data/CSV files",
  col.names=c("Close"))

#Define the asset to look at calcs for - ideally do this in a loop at the end
assetname <- "EAFE"
asset <- get(assetname)

#Define the subset period
SubsetPeriod <- "1973-01-31::2008-12-31" 
```

####Managing Risk 

Faber introduces a timing system for investors to use to manage the risk. Lets chart the 10 month simple moving average

```{r}
myChart_Theme <- chart_theme() #Create a chart_theme
myChart_Theme$col$line.col <- "blue"

SMAperiod <- 10

chart_Series(Cl(asset),
  name = paste(assetname," vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

# #why doesn't this for loop work????
# for(symbol in symbols[2:6]){
#   assetname <- symbol
#   asset <- get(assetname)
#   
#   chart_Series(Cl(asset),
#     name = paste(assetname," vs 10 Month Simple Moving Average",sep = ""),
#     theme=myChart_Theme,
#     type = "line",
#     subset = SubsetPeriod,
#     TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
#     )
# }
```

To - do 

 ylog = TRUE,
 ylim = c(40,6000),
 date.format = "%Y",
 major.ticks = "years",
 
* make it pull asset as variable, get log chart
* chart.posn (blotter) to show when in and out?
*add drawdown
* look at adding visualisation when its in / out of the market http://timelyportfolio.blogspot.co.za/2011/08/drawdown-visualization.html
* add legend

####Calculating returns
 

```{r, message=FALSE, warning=FALSE}
library(dplyr)

AllAssets <- cbind.xts(Cl(asset),
                       Cl(TBILLYIELDS))    

#create dataframe - tidyverse not compatible with xts?
AllAssets.df <- data.frame(date=index(AllAssets), coredata(AllAssets)) #, row.names = index(AllAssets))

#rename column for the Asset
colnames(AllAssets.df)[2] <- "Asset.Close"

#mutate new columns
AllAssets.df  <- mutate(AllAssets.df, 
  "10mSMA" = rollmean(Asset.Close,10,fill = 0,align = "right"),
  "Asset.ret" = c(0,diff(Asset.Close)/lag(Asset.Close)[-1]),
  "Rf.ret" = lag((TBILLYIELDS.Close/100)/12),
  "signal" = lag(ifelse(Asset.Close>`10mSMA`,1,0)),
  "Timing.ret" = ifelse(signal == 1,Asset.ret,Rf.ret) 
)

rownames(AllAssets.df) <- index(AllAssets)

#detach the packagae dplyr as it isn't compatible with other packages?
detach(package:dplyr)
```

####Calculating Stats

First lets create an xts of Returns
```{r}
SubsetPeriod <- "1972-12-31::2008-12-31"
AllAssets <- as.xts(AllAssets.df[,-1])
Returns <- cbind.xts(AllAssets$Asset.ret, AllAssets$Timing.ret)[SubsetPeriod]
colnames(Returns) <- c(assetname,"Timing")

#for calculating the sharpe ratio later
Rf.ret <- Return.calculate(TBILLS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod]

#create Cum returns for the chart
CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c(assetname,"Timing")
```

####Chart the returns

```{r}
chart.TimeSeries(CumReturns,
  main = paste(assetname," vs Timing Model ",substr(SubsetPeriod,1,4),"-",substr(SubsetPeriod,13,16),", Log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2),
  ylab = "",
  ylog = TRUE,
  ylim = c(50,7500),
  legend.loc = "left",
  major.ticks = "years",
  minor.ticks = FALSE)
```

todo
* chart with periods highlighted (similar to position chart)

####Drawdown chart

To give the reader a visual perspective of drawdowns we can chart

```{r}
chart.Drawdown(Returns,
  main = paste(assetname," vs Timing Model Drawdowns ",substr(SubsetPeriod,1,4),"-",substr(SubsetPeriod,13,16),", Non-log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2),
  ylab = "Drawdown",
  legend.loc = "bottom",
  major.ticks = "years",
  minor.ticks = FALSE)
```

to do - ensure same time period and x axis, print one above each other? area shading?


```{r}
stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               maxDrawdown(Returns,scale = 12,invert = FALSE)*100,
               c(nrow(subset(Returns, Returns$asset >= 0))/nrow(Returns),nrow(subset(Returns, Returns$Timing.ret >= 0))/nrow(Returns))*100)

colnames(stats) <- c("SP500","TIMING")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","% Positive Months")
round(stats,2)
```

To do:
*fix positive months
* SHARPE RF!!!!
* feed in correct Rf for period to get sharpe correct
* format percentages
* add $100 becomes and inflation CAGR
* loop for other asset classes
* add for another asset class
* confirm Rf / charpe sharpe to feed off Rf


####Chart Rolling Performance

```{r}
charts.RollingPerformance(Returns, 
                          main = "SP500 Total Returns vs Timing Total Returns (1973-2012)",
                          date.format = "%Y",
                          colorset = c(4,2),
                          ylog = FALSE,
                          minor.ticks =FALSE)
```

To do: 

* calculate returns for year before so rolling returns correct from day 1
* Look at bad data in 1975-1984
* change scale to 6 months?


#### Position chart

now can create position chart
```{r}

```
