---
title: "Replication of Faber's A Quantitative Approach to Tactical Asset Allocation - GTAA"
output: html_notebook
---

Faber applies his market timing rule to an asset allocation of US Stocks, foreign stocks, bonds, real estate and commodities. 

#### The code
```{r, message=FALSE, warning=TRUE, include=FALSE}
#Load the required packages
library(PerformanceAnalytics)
library(quantmod)
library(dplyr)
library(ggplot2)

#Set the symbols required
symbols <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","CPI","TBILLYIELDS")

#Load the data
getSymbols(symbols,
           src = "csv",
           dir="../Data/CSV files",
           col.names=c("Close"))
```

```{r}
#Create an xts of all assets' prices
AssetPrices <- cbind.xts(Cl(SP500),
                         Cl(EAFE),
                         Cl(US10YR),
                         Cl(GSCI),
                         Cl(NAREIT),
                         Cl(TBILLYIELDS))

AssetPrices <- AssetPrices["1972-01-31::2016-12-31"]

#Create dataframe to perform calculations (seems tidyverse not compatible with xts?)
TimingModelCalcs <- data.frame(date=index(AssetPrices), coredata(AssetPrices))
TimingModelCalcs  <- mutate(TimingModelCalcs,
  "SP500.SMA" =  rollmean(SP500.Close,10,fill = 0,align = "right"),
  "EAFE.SMA" =  rollmean(EAFE.Close,10,fill = 0,align = "right"),
  "US10YR.SMA" =  rollmean(US10YR.Close,10,fill = 0,align = "right"),
  "GSCI.SMA" =  rollmean(GSCI.Close,10,fill = 0,align = "right"),
  "NAREIT.SMA" =  rollmean(NAREIT.Close,10,fill = 0,align = "right"),
  "SP500.ret" =  c(0,diff(SP500.Close)/lag(SP500.Close)[-1]),
  "EAFE.ret" =  c(0,diff(EAFE.Close)/lag(EAFE.Close)[-1]),
  "US10YR.ret" =  c(0,diff(US10YR.Close)/lag(US10YR.Close)[-1]),
  "GSCI.ret" =  c(0,diff(GSCI.Close)/lag(GSCI.Close)[-1]),
  "NAREIT.ret" =  c(0,diff(NAREIT.Close)/lag(NAREIT.Close)[-1]),
  "RF.ret" =  lag((TBILLYIELDS.Close/100)/12),
  "SP500.signal" =  lag(ifelse(SP500.Close>=SP500.SMA,1,0)),
  "EAFE.signal" =  lag(ifelse(EAFE.Close>=EAFE.SMA,1,0)),
  "US10YR.signal" =  lag(ifelse(US10YR.Close>=US10YR.SMA,1,0)),
  "GSCI.signal" =  lag(ifelse(GSCI.Close>=GSCI.SMA,1,0)),
  "NAREIT.signal" = lag(ifelse(NAREIT.Close>=NAREIT.SMA,1,0)),
  "SP500.timingret" = ifelse(SP500.signal == 1,SP500.ret,RF.ret),
  "EAFE.timingret" = ifelse(EAFE.signal == 1,EAFE.ret,RF.ret),
  "US10YR.timingret" = ifelse(US10YR.signal == 1,US10YR.ret,RF.ret),
  "GSCI.timingret" = ifelse(GSCI.signal == 1,GSCI.ret,RF.ret),
  "NAREIT.timingret" = ifelse(NAREIT.signal == 1,NAREIT.ret,RF.ret),
  "GTAA.ret" = (SP500.timingret + EAFE.timingret + US10YR.timingret + GSCI.timingret + NAREIT.timingret)/5,
  "BUYANDHOLD.ret" = (SP500.ret + EAFE.ret + US10YR.ret + GSCI.ret + NAREIT.ret)/5
)

#Create xts of calculations to analyse performance
TimingModelCalcs.xts <- xts(TimingModelCalcs[,-1], order.by = TimingModelCalcs$date)
```

Notes:

* Technically rebalances monthly - should look at quarterly or annual rebalances?

### Replicating the research 1973-2012

#### Time invested

```{r}
TimeInvestedCalcs <- transmute(TimingModelCalcs,
  "Date" = date,
  "AssetsInvested" =  SP500.signal +  EAFE.signal + US10YR.signal + GSCI.signal + NAREIT.signal
)

TimeInvestedCalcs.xts <- xts(TimeInvestedCalcs[,-1], order.by = TimeInvestedCalcs$Date)

SubsetPeriod <- "1972-12-31::2012-12-31"
TimeInvestedCalcs.xts <- TimeInvestedCalcs.xts[SubsetPeriod]

#Tabulate and turn into data.frame
TimeInvestedStats <- as.data.frame(table(TimeInvestedCalcs.xts))
TimeInvestedStats <- transform(TimeInvestedStats,
                  "Percentage of Months" = prop.table(Freq))

colnames(TimeInvestedStats) <- c("Number of Positions","# of Months","% of Months")
TimeInvestedStats$`% of Months` <- round(TimeInvestedStats$`% of Months`,4)*100
rownames(TimeInvestedStats) <- c("0% Invested (all cash)",
                                 "20% Invested",
                                 "40% Invested",
                                 "60% Invested",
                                 "80% Invested",
                                 "100% Invested (fully invested)")

paste("On average the investor is ", 
      round(20*sum(c(0,1,2,3,4,5) * TimeInvestedStats$`# of Months`) / sum(TimeInvestedStats$`# of Months`),2), 
      "% invested", sep ="")

TimeInvestedStats
write.table(TimeInvestedStats, "clipboard", sep="\t", col.names=NA) #copies to clipboad for word/excel

SubsetPeriod <- "1972-12-31::2012-12-31"
chartdata.xts <- TimingModelCalcs.xts[SubsetPeriod]
chartdata.xts <- chartdata.xts[,c(0,18:22)]
chartdata.xts$total = c(0)
chartdata.xts$total = with(chartdata.xts,SP500.signal + EAFE.signal + US10YR.signal + NAREIT.signal + GSCI.signal)

plot.xts(chartdata.xts,
         multi.panel = TRUE,
         major.ticks = "years",
         grid.ticks.on = "years",
         yaxis.same = FALSE,
         main="",
         col = c("olivedrab","slateblue","cornflowerblue","gold2","orangered3","blue","dodgerblue2"))

#todo use ggplot to make better looking chart!
```

* need to format better


####extending

```{r}
TimeInvestedCalcs <- transmute(TimingModelCalcs,
  "Date" = date,
  "AssetsInvested" =  SP500.signal +  EAFE.signal + US10YR.signal + GSCI.signal + NAREIT.signal
)

TimeInvestedCalcs.xts <- xts(TimeInvestedCalcs[,-1], order.by = TimeInvestedCalcs$Date)

SubsetPeriod <- "1972-12-31::2016-12-31"
TimeInvestedCalcs.xts <- TimeInvestedCalcs.xts[SubsetPeriod]

#Tabulate and turn into data.frame
TimeInvestedStats <- as.data.frame(table(TimeInvestedCalcs.xts))
TimeInvestedStats <- transform(TimeInvestedStats,
                  "Percentage of Months" = prop.table(Freq))

colnames(TimeInvestedStats) <- c("Number of Positions","# of Months","% of Months")
TimeInvestedStats$`% of Months` <- round(TimeInvestedStats$`% of Months`,4)*100
rownames(TimeInvestedStats) <- c("0% Invested (all cash)",
                                 "20% Invested",
                                 "40% Invested",
                                 "60% Invested",
                                 "80% Invested",
                                 "100% Invested (fully invested)")

paste("On average the investor is ", 
      round(20*sum(c(0,1,2,3,4,5) * TimeInvestedStats$`# of Months`) / sum(TimeInvestedStats$`# of Months`),2), 
      "% invested", sep ="")

write.table(TimeInvestedStats, "clipboard", sep="\t", col.names=NA) #copies to clipboad for word/excel
```

For just 2013-2016
```{r}
TimeInvestedCalcs <- transmute(TimingModelCalcs,
  "Date" = date,
  "AssetsInvested" =  SP500.signal +  EAFE.signal + US10YR.signal + GSCI.signal + NAREIT.signal
)

TimeInvestedCalcs.xts <- xts(TimeInvestedCalcs[,-1], order.by = TimeInvestedCalcs$Date)

SubsetPeriod <- "2012-12-31::2016-12-31"
TimeInvestedCalcs.xts <- TimeInvestedCalcs.xts[SubsetPeriod]

#Tabulate and turn into data.frame
TimeInvestedStats <- as.data.frame(table(TimeInvestedCalcs.xts))
TimeInvestedStats <- transform(TimeInvestedStats,
                  "Percentage of Months" = prop.table(Freq))

colnames(TimeInvestedStats) <- c("Number of Positions","# of Months","% of Months")
TimeInvestedStats$`% of Months` <- round(TimeInvestedStats$`% of Months`,4)*100
rownames(TimeInvestedStats) <- c("0% Invested (all cash)",
                                 "20% Invested",
                                 "40% Invested",
                                 "60% Invested",
                                 "80% Invested",
                                 "100% Invested (fully invested)")

paste("On average the investor is ", 
      round(20*sum(c(0,1,2,3,4,5) * TimeInvestedStats$`# of Months`) / sum(TimeInvestedStats$`# of Months`),2), 
      "% invested", sep ="")

write.table(TimeInvestedStats, "clipboard", sep="\t", col.names=NA) #copies to clipboad for word/excel
```

####Performance Charts

```{r}
SubsetPeriod <- "1973-01-31::2016-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns["1973-01-31::2012-12-31"],
                 main = "Buy & Hold vs Timing Model, 1973-2012, log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = TRUE,
                 ylim = c(80,6000),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

chart.TimeSeries(CumReturns["1973-01-31::2012-12-31"],
                 main = "Buy & Hold vs Timing Model, 1973-2012, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(80,6000),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

chart.TimeSeries(CumReturns["1973-01-31::2016-12-31"],
                 main = "Buy & Hold vs Timing Model, 1973-2016, log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = TRUE,
                 ylim = c(80,6000),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

chart.TimeSeries(CumReturns["1973-01-31::2016-12-31"],
                 main = "Buy & Hold vs Timing Model, 1973-2016, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(80,6300),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

SubsetPeriod <- "2013-01-31::2016-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 1973-2012, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 #ylim = c(80,240),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```

```{r}
SubsetPeriod <- "1973-01-31::2012-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               100*maxDrawdown(Returns,invert = FALSE),
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```
to do: 

* why sharpe ratio is different - use RF!!!
* % positive months
* CAGR


```{r}
SubsetPeriod <- "2007-01-31::2016-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               100*maxDrawdown(Returns,invert = FALSE),
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```


### Yearly Returns

```{r}
SubsetPeriod <- "1972-12-31::2012-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
YearlyReturns <- cbind.xts(yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$BUYANDHOLD.ret[SubsetPeriod])),
                           yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$GTAA.ret[SubsetPeriod])))[-1,]

colnames(YearlyReturns) <- c("Buy & Hold","GTAA")

round(100*YearlyReturns,2)

YearlyStats <- rbind(Return.annualized(YearlyReturns)*100, 
               StdDev.annualized(YearlyReturns)*100, 
               SharpeRatio.annualized(YearlyReturns,Rf = 0.0541),
               maxDrawdown(YearlyReturns,invert = FALSE)*100,
               c(100*Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )

round(YearlyStats,2)
```

Notes:

* see how stats differ for annual - drawdown underreported so check daily

#### Since 2012

Let's see how the strategy has performed since 2012


```{r}
SubsetPeriod <- "2013-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")

chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 2013-2016, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(75,125),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```

```{r}
SubsetPeriod <- "1973-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","GTAA")
colnames(Returns) <- c("Buy & Hold","GTAA")
chart.TimeSeries(CumReturns,
                 main = "Buy & Hold vs Timing Model, 1973-2016, non-log scale",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "",
                 ylog = FALSE,
                 ylim = c(80,6500),
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)
```


```{r}
chart.Drawdown(Returns,
                 main = "Buy & Hold vs Timing Model Drawdowns, 1973-2016",
                 date.format = "%Y",
                 colorset = c(4,2),
                 ylab = "Drawdown",
                 legend.loc = "left",
                 major.ticks = "years",
                 minor.ticks = FALSE)

```


#### Yearly Returns since 2012
```{r}
SubsetPeriod <- "2012-12-31::2016-12-31" 
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]
YearlyReturns <- cbind.xts(yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$BUYANDHOLD.ret[SubsetPeriod])),
                           yearlyReturn(100*cumprod(1+TimingModelCalcs.xts$GTAA.ret[SubsetPeriod])))[-1,]

colnames(YearlyReturns) <- c("Buy & Hold","GTAA")
round(100*YearlyReturns,2)
```

#### Monthly Performance Stats since 2012

```{r}
SubsetPeriod <- "2013-01-31::2016-12-31"
Returns <- cbind.xts(TimingModelCalcs.xts$BUYANDHOLD.ret,TimingModelCalcs.xts$GTAA.ret)[SubsetPeriod]

stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = 0.0541/12),
               maxDrawdown(Returns,invert = FALSE)*100,
               c(100*Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod],scale = 12))
               )
colnames(stats) <- c("Buy & Hold","GTAA")
rownames(stats) <- c("Return","Volatility","Sharpe","MaxDD","Inflation CAGR")
round(stats,2)
```

Summary

* THE GTAA timing strategy continued to perform as it has in the past relative to the Buy and Hold strategy.
** From 2013 to 2016, although returns were slightly worse than the Buy and Hold there were with much less volatility and lower drawdowns.

```{r}
table.Drawdowns(Returns)
table.Drawdowns(Returns$GTAA.ret)
```

###testing out new averaging
####Including Property

AssetPrices <- cbind.xts(Cl(SP500),
                         Cl(EAFE),
                         Cl(US10YR),
                         Cl(GSCI),
                         Cl(NAREIT),
                         Cl(TBILLYIELDS))
                         
                      
```{r, message=FALSE, warning=FALSE}
#remove past data
rm(list = ls(envir = globalenv()),envir = globalenv()) #clear Vars from global enviroment

#Set Symbols
symbols <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","CPI","TBILLYIELDS")

#Import saved pricing data csv files as xts
getSymbols(symbols,
           src = "csv",
           dir="../Data/CSV files",
           col.names=c("Close"))

#Define subset dates for different period
SubsetPeriod.Reporting <- "1972-12-31::2016-12-31"
SubsetPeriod.Calculations <- "1972-01-31::2016-12-31"

AllAssets <- cbind.xts(Cl(TBILLS),
                       Cl(SP500),
                       Cl(EAFE),
                       Cl(US10YR),
                       Cl(GSCI),
                       Cl(NAREIT),
                       Cl(CPI)
                       )                       

AllAssets <- AllAssets[SubsetPeriod.Reporting]
colnames(AllAssets) <- symbols[-8]

#calculate returns and cum returns
AllAssets.ret <- Return.calculate(AllAssets)[-1,]
AllAssets.cumret <- 100*cumprod(1+ ROC(AllAssets, type = "discrete")[-1,])
#how do i add a row at the top with value of 100 for each? rbind?

chart.TimeSeries(AllAssets.cumret[SubsetPeriod.Reporting],
 main = paste("Figure X - SA Asset Class Returns, Log Scale",sep = ""),
 ylab = "",
 #ylog = TRUE,
 #ylim = c(100,250000),
 #date.format = "%Y",
 major.ticks = "years",
 legend.loc = "topleft",
 colorset = c("orangered3","olivedrab","slateblue","blue","gold2","dodgerblue2","cornflowerblue")
 #minor.ticks =FALSE
 )

#how do i change scale format!
```

```{r}
#Create xts for Returns
Returns <- AllAssets.ret[SubsetPeriod.Reporting]

#calculate statistics and store as "stats"
stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = AllAssets.ret$TBILLS),
               100*maxDrawdown(Returns,scale = 12,invert = FALSE),
               100*c(Return.annualized(Returns$CPI,scale = 12)))

#rename table rows/column names and format
colnames(stats) <- c("TBILLS","SP500","EAFE","US10YR","GSCI","NAREIT","CPI")    

rownames(stats) <- c("Return",
                     "Volatility",
                     paste("Sharpe (",round(stats[1,"TBILLS"],2),"%)", sep = ""),
                     "MaxDD",
                     "Inflation CAGR")

stats <- round(stats[,-7],2) #delete inflation column - change to 7 when including property.

#print
stats

#copies stats to clipboad for pasting into word/excel
#write.table(stats, "clipboard", sep="\t", col.names=NA) 
```


```{r}
myChart_Theme <- chart_theme() #Create a chart_theme
myChart_Theme$col$line.col <- "blue"

SMAperiod <- 10

chart_Series(Cl(SP500),
  name = paste("SP500 vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(EAFE),
  name = paste("MSCI World vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(US10YR),
  name = paste("US10YR vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(GSCI),
  name = paste("GSCI vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )

chart_Series(Cl(NAREIT),
  name = paste("NAREIT vs 10 Month Simple Moving Average",sep = ""),
  theme=myChart_Theme,
  type = "line",
  subset = SubsetPeriod.Reporting,
  TA = 'add_SMA(n=SMAperiod, on=1, col="red")'
  )
```


####Calculating returns

```{r, message=FALSE, warning=FALSE}
#load an additional library
library(dplyr)

#Create new all assets
AllAssets <- cbind.xts(Cl(SP500),
                       Cl(EAFE),
                       Cl(US10YR),
                       Cl(GSCI),
                       Cl(NAREIT),
                       Cl(TBILLYIELDS))   

AllAssets <- AllAssets[SubsetPeriod.Calculations]

#create dataframe - tidyverse not compatible with xts?
AllAssets.df <- data.frame(date=index(AllAssets), coredata(AllAssets)) #, row.names = index(AllAssets))

bandwidth <- 0.02
#mutate new columns
AllAssets.df  <- mutate(AllAssets.df,
  "RF.ret" =  c(0,lag((TBILLYIELDS.Close/100)/12)[-1]), 
  #is this right?

  "SP500.ret" =  c(0,diff(SP500.Close)/lag(SP500.Close)[-1]),
  
  "SP500.2m.SMA" =  rollmean(SP500.Close,2,fill = 0,align = "right"),
  "SP500.5m.SMA" =  rollmean(SP500.Close,5,fill = 0,align = "right"),
  "SP500.10m.SMA" =  rollmean(SP500.Close,10,fill = 0,align = "right"),
  
  "SP500.2m.signal" =  lag(ifelse(SP500.Close>=SP500.2m.SMA,1,0)),
  "SP500.5m.signal" =  lag(ifelse(SP500.Close>=SP500.5m.SMA,1,0)),
  "SP500.10m.signal" =  lag(ifelse(SP500.Close>=SP500.10m.SMA,1,0)),
  "SP500.2m.signal.delayed" =  lag(ifelse(SP500.Close>=SP500.2m.SMA,ifelse(SP500.2m.signal==1,1,0),0)),
  "SP500.5m.signal.delayed" =  lag(ifelse(SP500.Close>=SP500.5m.SMA,ifelse(SP500.5m.signal==1,1,0),0)),  
  "SP500.10m.signal.delayed" =  lag(ifelse(SP500.Close>=SP500.10m.SMA,ifelse(SP500.10m.signal==1,1,0),0)),
  
  "SP500.2m.timingret" = ifelse(SP500.2m.signal == 1,SP500.ret,RF.ret),
  "SP500.5m.timingret" = ifelse(SP500.5m.signal == 1,SP500.ret,RF.ret),
  "SP500.10m.timingret" = ifelse(SP500.10m.signal == 1,SP500.ret,RF.ret),
  "SP500.2m.timingret.delayed" = ifelse(SP500.2m.signal.delayed == 1,SP500.ret,RF.ret),
  "SP500.5m.timingret.delayed" = ifelse(SP500.5m.signal.delayed == 1,SP500.ret,RF.ret),
  "SP500.10m.timingret.delayed" = ifelse(SP500.10m.signal.delayed == 1,SP500.ret,RF.ret),
 
  "SP500.avg.timingret" = (SP500.2m.timingret + SP500.5m.timingret + SP500.10m.timingret)/3,
  "SP500.avg.timingret.delayed" = (SP500.2m.timingret.delayed + SP500.5m.timingret.delayed + SP500.10m.timingret.delayed)/3,  
  "SP500.avg.combo" = (SP500.avg.timingret + SP500.avg.timingret.delayed)/2,

  "EAFE.ret" =  c(0,diff(EAFE.Close)/lag(EAFE.Close)[-1]),
  
  "EAFE.2m.SMA" =  rollmean(EAFE.Close,2,fill = 0,align = "right"),
  "EAFE.5m.SMA" =  rollmean(EAFE.Close,5,fill = 0,align = "right"),
  "EAFE.10m.SMA" =  rollmean(EAFE.Close,10,fill = 0,align = "right"),
  
  "EAFE.2m.signal" =  lag(ifelse(EAFE.Close>=EAFE.2m.SMA,1,0)),
  "EAFE.5m.signal" =  lag(ifelse(EAFE.Close>=EAFE.5m.SMA,1,0)),
  "EAFE.10m.signal" =  lag(ifelse(EAFE.Close>=EAFE.10m.SMA,1,0)),
  "EAFE.2m.signal.delayed" =  lag(ifelse(EAFE.Close>=EAFE.2m.SMA,ifelse(EAFE.2m.signal==1,1,0),0)),
  "EAFE.5m.signal.delayed" =  lag(ifelse(EAFE.Close>=EAFE.5m.SMA,ifelse(EAFE.5m.signal==1,1,0),0)),  
  "EAFE.10m.signal.delayed" =  lag(ifelse(EAFE.Close>=EAFE.10m.SMA,ifelse(EAFE.10m.signal==1,1,0),0)),
  
  "EAFE.2m.timingret" = ifelse(EAFE.2m.signal == 1,EAFE.ret,RF.ret),
  "EAFE.5m.timingret" = ifelse(EAFE.5m.signal == 1,EAFE.ret,RF.ret),
  "EAFE.10m.timingret" = ifelse(EAFE.10m.signal == 1,EAFE.ret,RF.ret),
  "EAFE.2m.timingret.delayed" = ifelse(EAFE.2m.signal.delayed == 1,EAFE.ret,RF.ret),
  "EAFE.5m.timingret.delayed" = ifelse(EAFE.5m.signal.delayed == 1,EAFE.ret,RF.ret),
  "EAFE.10m.timingret.delayed" = ifelse(EAFE.10m.signal.delayed == 1,EAFE.ret,RF.ret),
  
  "EAFE.avg.timingret" = (EAFE.2m.timingret + EAFE.5m.timingret + EAFE.10m.timingret)/3,
  "EAFE.avg.timingret.delayed" = (EAFE.2m.timingret.delayed + EAFE.5m.timingret.delayed + EAFE.10m.timingret.delayed)/3,
  "EAFE.avg.combo" = (EAFE.avg.timingret + EAFE.avg.timingret.delayed)/2,
    
  "US10YR.ret" =  c(0,diff(US10YR.Close)/lag(US10YR.Close)[-1]),
  
  "US10YR.2m.SMA" =  rollmean(US10YR.Close,2,fill = 0,align = "right"),
  "US10YR.5m.SMA" =  rollmean(US10YR.Close,5,fill = 0,align = "right"),
  "US10YR.10m.SMA" =  rollmean(US10YR.Close,10,fill = 0,align = "right"),
  
  "US10YR.2m.signal" =  lag(ifelse(US10YR.Close>=US10YR.2m.SMA,1,0)),
  "US10YR.5m.signal" =  lag(ifelse(US10YR.Close>=US10YR.5m.SMA,1,0)),
  "US10YR.10m.signal" =  lag(ifelse(US10YR.Close>=US10YR.10m.SMA,1,0)),
  "US10YR.2m.signal.delayed" =  lag(ifelse(US10YR.Close>=US10YR.2m.SMA,ifelse(US10YR.2m.signal==1,1,0),0)),
  "US10YR.5m.signal.delayed" =  lag(ifelse(US10YR.Close>=US10YR.5m.SMA,ifelse(US10YR.5m.signal==1,1,0),0)),  
  "US10YR.10m.signal.delayed" =  lag(ifelse(US10YR.Close>=US10YR.10m.SMA,ifelse(US10YR.10m.signal==1,1,0),0)),
  
  "US10YR.2m.timingret" = ifelse(US10YR.2m.signal == 1,US10YR.ret,RF.ret),
  "US10YR.5m.timingret" = ifelse(US10YR.5m.signal == 1,US10YR.ret,RF.ret),
  "US10YR.10m.timingret" = ifelse(US10YR.10m.signal == 1,US10YR.ret,RF.ret),
  "US10YR.2m.timingret.delayed" = ifelse(US10YR.2m.signal.delayed == 1,US10YR.ret,RF.ret),
  "US10YR.5m.timingret.delayed" = ifelse(US10YR.5m.signal.delayed == 1,US10YR.ret,RF.ret),
  "US10YR.10m.timingret.delayed" = ifelse(US10YR.10m.signal.delayed == 1,US10YR.ret,RF.ret),
  
  "US10YR.avg.timingret" = (US10YR.2m.timingret + US10YR.5m.timingret + US10YR.10m.timingret)/3,
  "US10YR.avg.timingret.delayed" = (US10YR.2m.timingret.delayed + US10YR.5m.timingret.delayed + US10YR.10m.timingret.delayed)/3,
  "US10YR.avg.combo" = (US10YR.avg.timingret + US10YR.avg.timingret.delayed)/2,
  
  "GSCI.ret" =  c(0,diff(GSCI.Close)/lag(GSCI.Close)[-1]),
  
  "GSCI.2m.SMA" =  rollmean(GSCI.Close,2,fill = 0,align = "right"),
  "GSCI.5m.SMA" =  rollmean(GSCI.Close,5,fill = 0,align = "right"),
  "GSCI.10m.SMA" =  rollmean(GSCI.Close,10,fill = 0,align = "right"),
  
  "GSCI.2m.signal" =  lag(ifelse(GSCI.Close>=GSCI.2m.SMA,1,0)),
  "GSCI.5m.signal" =  lag(ifelse(GSCI.Close>=GSCI.5m.SMA,1,0)),
  "GSCI.10m.signal" =  lag(ifelse(GSCI.Close>=GSCI.10m.SMA,1,0)),
  "GSCI.2m.signal.delayed" =  lag(ifelse(GSCI.Close>=GSCI.2m.SMA,ifelse(GSCI.2m.signal==1,1,0),0)),
  "GSCI.5m.signal.delayed" =  lag(ifelse(GSCI.Close>=GSCI.5m.SMA,ifelse(GSCI.5m.signal==1,1,0),0)),  
  "GSCI.10m.signal.delayed" =  lag(ifelse(GSCI.Close>=GSCI.10m.SMA,ifelse(GSCI.10m.signal==1,1,0),0)),
   
  "GSCI.2m.timingret" = ifelse(GSCI.2m.signal == 1,GSCI.ret,RF.ret),
  "GSCI.5m.timingret" = ifelse(GSCI.5m.signal == 1,GSCI.ret,RF.ret),
  "GSCI.10m.timingret" = ifelse(GSCI.10m.signal == 1,GSCI.ret,RF.ret),
  "GSCI.2m.timingret.delayed" = ifelse(GSCI.2m.signal.delayed == 1,GSCI.ret,RF.ret),
  "GSCI.5m.timingret.delayed" = ifelse(GSCI.5m.signal.delayed == 1,GSCI.ret,RF.ret),
  "GSCI.10m.timingret.delayed" = ifelse(GSCI.10m.signal.delayed == 1,GSCI.ret,RF.ret),

  "GSCI.avg.timingret" = (GSCI.2m.timingret + GSCI.5m.timingret + GSCI.10m.timingret)/3,
  "GSCI.avg.timingret.delayed" = (GSCI.2m.timingret.delayed + GSCI.5m.timingret.delayed + GSCI.10m.timingret.delayed)/3,
  "GSCI.avg.combo" = (GSCI.avg.timingret + GSCI.avg.timingret.delayed)/2,

  "NAREIT.ret" =  c(0,diff(NAREIT.Close)/lag(NAREIT.Close)[-1]),
  
  "NAREIT.2m.SMA" =  rollmean(NAREIT.Close,2,fill = 0,align = "right"),
  "NAREIT.5m.SMA" =  rollmean(NAREIT.Close,5,fill = 0,align = "right"),
  "NAREIT.10m.SMA" =  rollmean(NAREIT.Close,10,fill = 0,align = "right"),
  
  "NAREIT.2m.signal" =  lag(ifelse(NAREIT.Close>=NAREIT.2m.SMA,1,0)),
  "NAREIT.5m.signal" =  lag(ifelse(NAREIT.Close>=NAREIT.5m.SMA,1,0)),
  "NAREIT.10m.signal" =  lag(ifelse(NAREIT.Close>=NAREIT.10m.SMA,1,0)),
  "NAREIT.2m.signal.delayed" =  lag(ifelse(NAREIT.Close>=NAREIT.2m.SMA,ifelse(NAREIT.2m.signal==1,1,0),0)),
  "NAREIT.5m.signal.delayed" =  lag(ifelse(NAREIT.Close>=NAREIT.5m.SMA,ifelse(NAREIT.5m.signal==1,1,0),0)),  
  "NAREIT.10m.signal.delayed" =  lag(ifelse(NAREIT.Close>=NAREIT.10m.SMA,ifelse(NAREIT.10m.signal==1,1,0),0)),
   
  "NAREIT.2m.timingret" = ifelse(NAREIT.2m.signal == 1,NAREIT.ret,RF.ret),
  "NAREIT.5m.timingret" = ifelse(NAREIT.5m.signal == 1,NAREIT.ret,RF.ret),
  "NAREIT.10m.timingret" = ifelse(NAREIT.10m.signal == 1,NAREIT.ret,RF.ret),
  "NAREIT.2m.timingret.delayed" = ifelse(NAREIT.2m.signal.delayed == 1,NAREIT.ret,RF.ret),
  "NAREIT.5m.timingret.delayed" = ifelse(NAREIT.5m.signal.delayed == 1,NAREIT.ret,RF.ret),
  "NAREIT.10m.timingret.delayed" = ifelse(NAREIT.10m.signal.delayed == 1,NAREIT.ret,RF.ret),

  "NAREIT.avg.timingret" = (NAREIT.2m.timingret + NAREIT.5m.timingret + NAREIT.10m.timingret)/3,
  "NAREIT.avg.timingret.delayed" = (NAREIT.2m.timingret.delayed + NAREIT.5m.timingret.delayed + NAREIT.10m.timingret.delayed)/3,
  "NAREIT.avg.combo" = (NAREIT.avg.timingret + NAREIT.avg.timingret.delayed)/2,

  "BuyandHold.ret" = (SP500.ret + EAFE.ret + US10YR.ret + GSCI.ret + NAREIT.ret)/5,
  "Timing.2m.ret" = (SP500.2m.timingret + EAFE.2m.timingret + US10YR.2m.timingret + GSCI.2m.timingret + NAREIT.2m.timingret)/5,
  "Timing.5m.ret" = (SP500.5m.timingret + EAFE.5m.timingret + US10YR.5m.timingret + GSCI.5m.timingret + NAREIT.5m.timingret)/5,
  "Timing.ret" = (SP500.10m.timingret + EAFE.10m.timingret + US10YR.10m.timingret + GSCI.10m.timingret + NAREIT.10m.timingret)/5,
  "DelayedTiming.ret" = (SP500.10m.timingret.delayed + EAFE.10m.timingret.delayed + US10YR.10m.timingret.delayed + GSCI.10m.timingret.delayed 
                         + NAREIT.10m.timingret.delayed)/5,
  "Avg.Timing.ret" = (SP500.avg.timingret + EAFE.avg.timingret + US10YR.avg.timingret + GSCI.avg.timingret + NAREIT.avg.timingret)/5,
  "Avg.DelayedTiming.ret" = (SP500.avg.timingret.delayed + EAFE.avg.timingret.delayed + 
                            US10YR.avg.timingret.delayed + NAREIT.avg.timingret.delayed + GSCI.avg.timingret.delayed)/5,
  "Avg.Combo.ret" = (SP500.avg.combo + EAFE.avg.combo + 
                            US10YR.avg.combo + GSCI.avg.combo + NAREIT.avg.combo)/5
  
  )

rownames(AllAssets.df) <- index(AllAssets)

#Create xts of calculations to analyse performance
AllAssets.xts <- xts(AllAssets.df[,-1], order.by = AllAssets.df$date)

#detach the packagae dplyr as it isn't compatible with other packages?
detach(package:dplyr)
```

#### SP500 Timing Strategy Comparisons

```{r}
#for calculating the sharpe ratio later
Rf.ret <- Return.calculate(TBILLYIELDS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod.Reporting]

#MSCI World
Returns <- cbind.xts(AllAssets.xts$SP500.ret, 
                     AllAssets.xts$SP500.10m.timingret, 
                     AllAssets.xts$SP500.10m.timingret.delayed, 
                     AllAssets.xts$SP500.avg.timingret,
                     AllAssets.xts$SP500.avg.timingret.delayed,
                     AllAssets.xts$SP500.avg.combo)[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy and Hold","Timing","Timing Delayed","Avg Timing","Avg Timing Delayed","Avg Combo")
colnames(Returns) <- c("Buy and Hold","Timing","Timing Delayed","Avg Timing","Avg Timing Delayed","Avg Combo")

#how do i add earlier row and make it 100

#as.numeric(substr(SubsetPeriod,1,4))+1
chart.TimeSeries(CumReturns,
  main = paste("Buy and Hold vs Timing vs Timing Avg, ",
               substr(SubsetPeriod.Reporting,1,4),"-",
               substr(SubsetPeriod.Reporting,13,16),
               ", Log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(50,1000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE)

chart.Drawdown(Returns,#[,-1], to exclude B&H
  main = paste("Buy and Hold vs Timing vs Timing Avg",substr(SubsetPeriod.Reporting,1,4),"-",substr(SubsetPeriod.Reporting,13,16),", Non-log Scale",sep = ""),
  date.format = "%Y",
  colorset = c(4,2,3,5,6),
  ylab = "Drawdown",
  legend.loc = "bottomright",
  major.ticks = "years",
  minor.ticks = FALSE)

```

```{r}
Rf.ret <- Return.calculate(TBILLS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod.Reporting]

stats <- rbind(Return.annualized(Returns,scale = 12)*100, 
               StdDev.annualized(Returns,scale = 12)*100, 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               maxDrawdown(Returns,scale = 12,invert = FALSE)*100,
               
               # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               #Information Ratio
               InformationRatio(Returns, Returns$"Buy and Hold"),
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               #Calmar Ratio
               CalmarRatio(Returns["2014::2017"], scale = 12)
               
               )
               
colnames(stats) <- c("Buy and Hold","Timing","Timing Delayed","Average Timing","Average Timing Delayed","Avg Combo")
rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe",
                     "MaxDD",
                     # "% Positive Months",
                     # "% Months invested in the Asset",
                     # "% Positive Months when invested",
                     "Sortino Ratio",
                     "Information Ratio",
                     "Ulcer Index",
                     "Calmar Ratio")

round(stats,2)
write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```

####GTAA Performance Charts - Buy and hold vs Timing vs Diversifed portfolio of strategies

```{r}
#need to add trading bands when complete - if time look at a mean reversion strat
Rf.ret <- Return.calculate(TBILLS)[-1,]
Rf.ret <- Rf.ret[SubsetPeriod.Reporting]

Returns <- cbind.xts(AllAssets.xts$BuyandHold.ret,
                     AllAssets.xts$Timing.ret,
                     #AllAssets.xts$DelayedTiming.ret,
                     #AllAssets.xts$Avg.Timing.ret,
                     #AllAssets.xts$Avg.DelayedTiming.ret,
                     AllAssets.xts$Avg.Combo.ret)[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])

colnames(CumReturns) <- c("Buy & Hold",
                       "Timing",
                       #"Delayed Timing","Avg Timing","Avg Delayed Timing",
                       "Avg Combo")


chart.TimeSeries(CumReturns,
  main = "Figure X - Timing Model Comparison, Log Scale",
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(100,76000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE,
  yaxis = TRUE)


colnames(Returns) <- colnames(CumReturns)

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               100*maxDrawdown(Returns,invert = FALSE),

               #Calmar Ratio
               CalmarRatio(Returns, scale = 12), #orCalmarRatio(Returns["2014::2017"], scale = 12)
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod.Reporting],scale = 12))
               
               )

colnames(stats) <- colnames(Returns)

rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe", #what %?
                     "MaxDD",
                     "Calmar Ratio",
                     "Ulcer Index",
                     "Sortino Ratio",
                     "Inflation CAGR")

round(stats,2)
#write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```

####Delaying Entry

```{r, message=FALSE, warning=FALSE}
Returns <- cbind.xts(AllAssets.xts$BuyandHold.ret,
                     AllAssets.xts$Timing.ret,
                     AllAssets.xts$DelayedTiming.ret,
                     AllAssets.xts$Avg.Timing.ret,
                     AllAssets.xts$Avg.DelayedTiming.ret
                     )[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","Timing","Delayed Timing","Avg Timing","Avg Delayed Timing")

chart.TimeSeries(CumReturns,
  main = "Figure X - Timing Model Comparison, Log Scale", #note log not working on new charts
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(100,76000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE,
  yaxis = TRUE)

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               100*maxDrawdown(Returns,invert = FALSE),

               #Calmar Ratio
               CalmarRatio(Returns, scale = 12), #orCalmarRatio(Returns["2014::2017"], scale = 12)
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod.Reporting],scale = 12))
               
               )

colnames(stats) <- colnames(CumReturns)

rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe", #what %?
                     "MaxDD",
                     "Calmar Ratio",
                     "Ulcer Index",
                     "Sortino Ratio",
                     "Inflation CAGR")

round(stats,2)
#write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```

####Diversification of Timing Signal

```{r, message=FALSE, warning=FALSE}
Returns <- cbind.xts(AllAssets.xts$BuyandHold.ret,
                     AllAssets.xts$Timing.2m.ret,
                     AllAssets.xts$Timing.5m.ret,
                     AllAssets.xts$Timing.ret,
                     AllAssets.xts$Avg.Timing.ret)[SubsetPeriod.Reporting]

CumReturns <- 100*cumprod(1+Returns[-1,])
colnames(CumReturns) <- c("Buy & Hold","2m Timing","5m Timing","10m Timing","Avg Timing")

chart.TimeSeries(CumReturns,
  main = "Figure X - Timing Model Comparison, Log Scale", #note log not working on new charts
  date.format = "%Y",
  colorset = c(4,2,3,5,6,7),
  ylab = "",
  ylog = TRUE,
  #ylim = c(100,76000),
  legend.loc = "topleft",
  major.ticks = "years",
  minor.ticks = FALSE,
  yaxis = TRUE)

stats <- rbind(100*Return.annualized(Returns,scale = 12), 
               100*StdDev.annualized(Returns,scale = 12), 
               SharpeRatio.annualized(Returns,Rf = Rf.ret$TBILLS.Close),
               100*maxDrawdown(Returns,invert = FALSE),

               #Calmar Ratio
               CalmarRatio(Returns, scale = 12), #orCalmarRatio(Returns["2014::2017"], scale = 12)
               
               #Ulcer Index
               100*UlcerIndex(Returns),
               
               # Sortino
               SortinoRatio(Returns, MAR = 0),
               
               100*c(Return.annualized(Return.calculate(Cl(CPI))[SubsetPeriod.Reporting],scale = 12))
               
               )

colnames(stats) <- colnames(CumReturns)

rownames(stats) <- c("Return",
                     "Volatility",
                     "Sharpe", #what %?
                     "MaxDD",
                     "Calmar Ratio",
                     "Ulcer Index",
                     "Sortino Ratio",
                     "Inflation CAGR")

round(stats,2)
#write.table(round(stats,4), "clipboard", sep="\t", col.names=NA)
```


Correlation chart
```{r}
#load closing pricings
CorrelationData <- do.call(cbind,list(Cl(SP500),Cl(EAFE),Cl(US10YR),Cl(GSCI),Cl(NAREIT)))
CorrelationData <- CorrelationData[SubsetPeriod.Reporting]

#Convert from prices to log prices
CorrelationData.ret <- Return.calculate(CorrelationData)[-1,]

BITCOIN.ret <- log(Cl(BITCOIN))

BITCOIN.ret <- BITCOIN.ret["2010-12-31::2016-12-31"]

chart.RollingCorrelation(CorrelationData.ret, CorrelationData.ret$SP500, width = 24, legend.loc = "bottomleft")
```

